\documentclass{article}
\usepackage[english]{babel}
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Book F1 - 2024}
\author{AIMI Laora}
\date{}

\begin{document}
\maketitle


\section*{Introduction}

This document is a thorough report on the 2024 Formula 1 World Championship from a race-by-race perspective. Each Grand Prix consists of two main sections:

\begin{itemize}
    \item \textbf{Circuit Analysis} — The circuit layout is presented, along with its specific character, strategic challenges (specific braking zones, tyre degradation, overtaking zones, DRS zones, and some weather context).
    \item \textbf{Race Analysis} — The section provides a summary of qualifying and race results, the major incidents, the strategies the teams used, the trends in performance, and the implications of the championship. Each analysis ends with a Takeaway, identifying the key factors from the results of the event, primarily for lessons learned.
\end{itemize}

The objective is not only to record the results of the 2024 season, but also to identify broader
performance trends, strategic choices, and turning points that shaped the battle between drivers
and constructors.

The end of season review includes a global synthesis outlines:
\begin{itemize}
    \item The main competitive trends of the year,
    \item The biggest surprises and disappointments,
    \item A team-by-team evaluation of performance.
\end{itemize}

This contributes to summarising the full season, comparing an overview of both the technical and strategic distance traveled by the racers and constructors together over the course of a season.



\include{1.Bahrain}
\include{2.Saudi_Arabia}
\include{3.Australia}
\include{4.Japan}
\include{5.China}
\include{6.Miami}
\include{7.Emilia_Romagna}
\include{8.Monaco}
\include{9.Canada}
\include{10.Spain}
\include{11.Austria}
\include{12.Great_Britain}
\include{13.Hungary}
\include{14.Belgium}
\include{15.Netherlands}
\include{16.Italy}
\include{17.Azerbaijan}
\include{18.Singapore}
\include{19.United_States}
\include{20.Mexico}
\include{21.Brazil}
\include{22.Las_Vegas}
\include{23.Qatar}
\include{24.Abu_Dhabi}


\section*{Season Conclusion}

\subsection*{General Trends}

The 2024 Formula 1 season was marked by a monumental shift in the power of the Constructors' Championship.
After years of domination by Mercedes and Red Bull, McLaren became the new standard and they won their first Constructors' Title since 1998.
Ferrari displayed consistency and competitiveness throughout the year, while Red Bull suffered from strategic and reliability issues despite Verstappen conquering his fourth consecutive Drivers' Crown. 
Mercedes showed flashes of pace, but inconsistency did not allow for any challenge toward to the top. 
The battle remained intense in the midfield, with Alpine, Haas, and Racing Bulls all fighting for crucial points until the very final race.

\subsection*{Surprises and Highlights}

\begin{itemize}
    \item \textbf{McLaren Resurgence:} Lando Norris achieved four victories and multiple pole positions, supported by Oscar Piastri’s strong season, making McLaren the reference team of 2024.
    \item \textbf{Ferrari’s Consistency:} Charles Leclerc delivered remarkable comebacks (notably Abu Dhabi) and Carlos Sainz closed his Ferrari chapter with steady podiums, giving the team its best campaign in years.
    \item \textbf{Red Bull’s Decline:} While Verstappen secured the Drivers’ title early, the team struggled with tyre wear, strategy missteps, and Sergio Pérez’s lack of competitiveness.
    \item \textbf{Hamilton’s Farewell:} Lewis Hamilton ended his Mercedes era with memorable drives, preparing for a historic move to Ferrari in 2025.
    \item \textbf{Midfield Surprises:} Pierre Gasly’s late-season heroics secured Alpine P6 in the standings. Haas showed progress with Nico Hülkenberg’s qualifying performances and Magnussen’s fastest lap in Abu Dhabi. 
    \item \textbf{Rookies on Stage:} Jack Doohan debuted for Alpine, Liam Lawson and Franco Colapinto scored appearances, while Arthur Leclerc made headlines with his FP1 participation.
\end{itemize}

\subsection*{Team-by-Team Summary}

\begin{itemize}
    \item \textbf{McLaren (Champions, 666 pts):} The revelation of 2024. Norris emerged as Verstappen’s main challenger, while Piastri consolidated McLaren’s return to the top.
    \item \textbf{Ferrari (2nd, 652 pts):} Consistent and fast, but just short of the Constructors’ crown. Leclerc’s form was outstanding, Sainz reliable until his farewell.
    \item \textbf{Red Bull (3rd, 589 pts):} Verstappen dominated individually but Pérez’s poor results cost them dearly. Strategic weaknesses were exposed.
    \item \textbf{Mercedes (4th, 468 pts):} A year of transition. Russell consistent, Hamilton brilliant in moments, but overall lack of pace prevented title contention.
    \item \textbf{Aston Martin (5th, 94 pts):} Alonso continued to extract results, but the car regressed compared to 2023. Stroll failed to deliver significant points.
    \item \textbf{Alpine (6th, 65 pts):} Gasly carried the team with key points late in the season. Ocon’s departure and Doohan’s debut marked a changing era.
    \item \textbf{Haas (7th, 58 pts):} Solid step forward. Hülkenberg competitive in qualifying, Magnussen opportunistic. Midfield progress clear.
    \item \textbf{Racing Bulls (8th, 46 pts):} Tsunoda dependable, Ricciardo underperformed before Lawson’s chance. A team in search of identity.
    \item \textbf{Williams (9th, 17 pts):} Albon remained the leading force, Colapinto debuted with promise. Still lacking consistency to fight higher.
    \item \textbf{Kick Sauber (10th, 4 pts):} A tough season. Zhou and Bottas endured a difficult year. Transition toward Audi in 2026 looms.
\end{itemize}

\subsection*{Final Takeaway}

2024 will be remembered as the year of McLaren’s resurgence, Norris’ emergence as a true championship contender, and Verstappen’s consolidation as a four-time World Champion. 
The season closed a historic chapter with Hamilton’s farewell to Mercedes, while setting the stage for 2025 with Ferrari’s ambitious lineup and a revitalized grid dynamic.


\end{document}
